Supplement

### 2023-07-03 paper/manuscript.Rmd
more tau and citation tweaks

tau_predIntcount <- d |> filter(!is.na(predInt_from_d)) |> filter(predInt_with_tau) |> nrow()
tau_predInttotal <- d |> filter(!is.na(predInt_from_d))  |> nrow()

tau_pct <- tau_predIntcount/tau_predInttotal*100
# with tau 73 in / 41 out (64%)

>>>>

tau_predIntcount <- d |> filter(include %in% c("stats")) |> filter(!is.na(predInt_from_d)) |> filter(predInt_with_tau) |> nrow()
tau_predInttotal <- d |> filter(include %in% c("stats")) |> filter(!is.na(predInt_from_d))  |> nrow()

tau_pct <- tau_predIntcount/tau_predInttotal*100

### 2023-07-03 paper/manuscript.tex
more tau and citation tweaks

Across the 176 studies, the average subjective replication score was 49\%, which we can interpret as an overall subjective replication rate. 46\% (62/136) of the studies had replication outcomes within the prediction interval of the original outcome. The median p\_original value was 0.03 representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent. Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score. Some studies replicated withed similar size effects to the original, and others failed to replicate, with replication effect sizes near zero. On average, there was a diminution of effect sizes from original to replication. This pattern of results is consistent with the pattern of results found in RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).

@@

\leavevmode\vadjust pre{\hypertarget{ref-openscienceconsortium2015}{}}%
Open Science Consortium (2015) Estimating the reproducibility of psychological science. \emph{Science}

>>>>

Across the 176 studies, the average subjective replication score was 49\%, which we can interpret as an overall subjective replication rate. 46\% (62/136) of replications has outcomes with point-estimates within the prediction interval of the original outcome. The median p\_original value on the original and replication point-estimates coming from the same distribution was 0.03, representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent. Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score. Some studies replicated withed similar size effects to the original, and others failed to replicate, with replication effect sizes near zero. On average, there was a diminution of effect sizes from original to replication. This pattern of results is consistent with the pattern of results found in RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).

Some multi-site replication projects have found heterogeneity in effect sizes across replication sites (\protect\hyperlink{ref-klein2018}{Klein et al. 2018}, \protect\hyperlink{ref-ebersole2020}{Ebersole et al. 2020}, \protect\hyperlink{ref-olsson2020}{Olsson-Collentine et al. 2020}). We calculated how often the original and replication results were distributionally consistent. If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects would be the same as the average level heterogeneity found in Olsson-Collentine et al. (\protect\hyperlink{ref-olsson2020}{2020}) (tau=.21 in SMD units), then 64.3\% (72/112) of replications are distributionally consistent with the original. More work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replications.

{[}what was I supposed to say about heterogeneity, and is this the right place for it?{]}

@@

\leavevmode\vadjust pre{\hypertarget{ref-olsson2020}{}}%
Olsson-Collentine A, Assen MA van, Wicherts J (2020) Heterogeneity in direct replications in psychology and its association with effect size.

\leavevmode\vadjust pre{\hypertarget{ref-openscienceconsortium2015}{}}%
Open Science Consortium (2015) \href{https://www.science.org/doi/full/10.1126/science.aac4716?casa_token=IJ35TwwlcjsAAAAA\%3AqiP68QbVAHleIg9zD3WugKWuV6Oa5rswS0VQnDsCq5I14ME4WIQabNGVD_T6SBSuAt6voVHNnWc0sw}{Estimating the reproducibility of psychological science}. \emph{Science}

### 2023-07-03 paper/supplement.Rmd
more tau and citation tweaks

```{r, include=F, echo=F}
d |> select(starts_with("pred") | starts_with("p_orig"))

d |> filter(!is.na(predInt)) |> count(predInt)
#using predInt as reported 62 in interval, 72 not (45% rep)

#of those with SMD predInts
d |> filter(!is.na(predInt_from_d)) |> count(predInt)
# using predInt 44 in / 70 out (38%)
d |> filter(!is.na(predInt_from_d)) |> count(predInt_from_d)
# 34 in /80 out (30%)
d |> filter(!is.na(predInt_from_d)) |> count(predInt_with_tau)
# with tau 73 in / 41 out (64%)

d |> filter(!is.na(predInt)) |> summarise(median(p_orig))
#median .03

#of those with SMD predInts
d |> filter(!is.na(predInt_from_d)) |>summarise(median(p_orig))
# median .01
d |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_from_d))
# median .001
d |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_with_tau))
# median .15
```

>>>>

```{r, echo=F}

d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> count(predInt)

#of those with SMD predInts
d |>filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> count(predInt)
d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> count(predInt_from_d)
d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> count(predInt_with_tau)

d |> filter(include %in% c("stats", "pred_int")) |> filter(!is.na(predInt)) |> summarise(median(p_orig))
#median .03

#of those with SMD predInts
d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |>summarise(median(p_orig))
d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_from_d))
d |> filter(include=="stats") |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_with_tau))
```
